Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-07 paper/paper.tex
pass on V.B

Table~\ref{tab:cross-testing} shows the number of failures for each
pair of test suite and engine. The first column shows the test suites
and the first row shows the engines that run those tests. We use a
dash (``-'') to indicate that we did not consider the combinations
that associated a test suite with its parent engine; failures in those
cases would either indicate regressions or flaky tests as opposed to
an unknown bug for that engine. We did not run the test cases that
fail on its parent engine in any other engines; we wanted all tests to
pass on their parent engine as a failure in that case would be a
stronger indicative of a bug. In total, 64 test cases were discarded
for that reason--6 from \jsc{} and 58 from \smonkey. In total, 7,029
tests (\ie{}, 28369-31276-64) were considered in this experiment.  We
observed from the table that, considering this dataset, the Mozilla
\smonkey\ was the engine that failed the least whereas the Microsoft
engine \chakra\ failed the most. The \smonkey\ test suite also
revealed more failures than any other, perhaps as expected,
considering that it is the suite with more tests (see
Table~\ref{tab:test-suites}). This suggests that the investiment in
testing paid off in this case.

@@

The piecharts from Figure~\ref{fig:piecharts-transplantation} show the
false and true positives observed with test transplantation. The top
piechart shows false alarms.  It is important to stress that all the
``transplanted'' tests should have passed in these cases. The absolute
number of tests is shown in parentheses to the right side of the
explanation for the false positive. The sources of false alarm are as
follows:

\begin{itemize}
  \item \textbf{Undefined.} Implementation-dependent behavior as per
    ECMA262 specification~\cite{ecmas262-spec}. For example, 
    \Igor{a test from JerryScript suite uses a function \CodeIn{Number.toPrecision([precision])}
    that returns a string representing the number object in
    fixed-point or exponential notation rounded to precision. According to ES specifications(cite)
    built-ins that involves Math functions are implementation-dependent 
    approximation to the real value.
    }
  \item \textbf{Timeout/OME\footnote{ome is for out of memory
      error.}.} Because target engine does not optimize code as the
    original engine did, test fails to finish at the time limit
    specified in the test or runs out of memory. For example, we found
    that only \jsc{} implements tail-call optimization to avoid tail
    recursion.
  \item \textbf{Not implemented.} Test fails because it covers
    function in the spec which is yet to be implemented. For example,
    at the time of writing, Chakra did not implement various
    properties from the \mcodeid{Symbol} object. A test that refers to
    this object will fail in \chakra{}.
  \item \textbf{Future Feature.} Test fails because it uses a feature
    that is available in the original engine, but still not standard,
    and the target engine does not support that feature. For example,
    \Fix{XXX} \Igor{Creio que neste experimento, essa funcao nao vai 
    aparecer. Identificamos isto em alguns testes da suite test262(nao estamos utilizando ela aqui).}
  \item \textbf{Error message mismatch.} Test fails because it
    compares an error message, which is not portable across
    engines. For example, \Igor{
      a test from the engine \jsc{} uses an assert function called
      \CodeIn{shouldThrow} that expects an specific error message. In this test, 
      all engines throws the Error as expected, however only the message 
      on \jsc{} engine match with the string expected in the test case.
    }
\end{itemize}

@@

Table~\ref{tab:false-positives} shows the distribution of false
positives per source. A false positive is a bucket that did not lend
itself in a bug report. The sources of imprecision are as defined in
Section~\ref{sec:transplantation} with the addition of one, which
emerges with fuzzing. The source ``invalid input'' indicates that the
test violated some part of the specification. For example, the test
indirectly invoked some function with unexpected arguments\Fix{provide
  concrete example}.

\begin{table}[t]
  \centering
  \caption{\label{tab:false-positives}Distribution of false
    positives buckets per source.}
  \begin{tabular}{crr}
    \toprule
    & \radamsa\ & \quickfuzz\ \\
    Undefined & - & - \\
    Timeout/OME & - & - \\
    Not Implemented & - & - \\
    Future Feature & - & - \\
    Error Message Mismatch & - & - \\    
    Invalid Input & - & - \\    
    \bottomrule     
  \end{tabular}
\end{table}

>>>>

Table~\ref{tab:cross-testing} shows the number of failures for each
pair of test suite and engine. The first column shows the test suites
and the first row shows the engines that run those tests. We use a
dash (``-'') to indicate that we did not consider the combinations
that associated a test suite with its parent engine; failures in those
cases would either indicate regressions or flaky tests as opposed to
an unknown bug for that engine. We did not run the test cases that
fail on its parent engine in any other engines; we wanted all tests to
pass on their parent engine as a failure in that case would be a
stronger indicative of a bug. In total, 64 test cases were discarded
for that reason--6 from \jsc{} and 58 from \smonkey. In total, 7,029
test files (\ie{}, 38369-31276-64) were considered in this experiment,
which involved 24,922 test runs (\ie, (7029*4)-1021-57-2116).  Of
these, 812 failures were observed (3.25\% of the runs) across
\textbf{543} distinct files (7.72\% of the files). We analyzed each of
these file in separate to identify if the failure was fault-revealing
or a false positive.

We observed from the table that, considering this dataset, the Mozilla
\smonkey\ was the engine that failed the least whereas the Microsoft
engine \chakra\ failed the most. The \smonkey\ test suite also
revealed more failures than any other, perhaps as expected,
considering that it is the suite with more tests (see
Table~\ref{tab:test-suites}).

%% This suggests that the investiment in
%% testing paid off in this case.

@@

The piecharts from Figure~\ref{fig:piecharts-transplantation} show the
false and true positives observed with test transplantation. The top
piechart shows false alarms.  It is important to stress that all the
``transplanted'' tests should have passed in these cases. The absolute
number of tests in each category is shown in parentheses to the
right-side of the label of a slice, nameing the source of false
positive. The sources are as follows:

\begin{itemize}
  \item \textbf{Undefined Behavior.} False positives of this kind are
    manifested when tests cover implementation-dependent behavior, as
    defined in the ECMA262 specification~\cite{ecmas262-spec}. For
    example, one of the tests from \jerry\ uses the function
    \CodeIn{Number.toPrecision([precision])}, which translates a
    number to a string, considering a given number of significant
    digits. The floating-point approximation of the real value is
    implementation-dependent, making the test to pass only in
    \chakra\ for that test.

  \item \textbf{Timeout/OME\footnote{ome is for out of memory
      error.}.} False positives of this kind manifest when the target
    engine that runs the test do not optimize code as the original
    engine. For that, tests fail to finish at the time budget or runs
    out of memory.\Comment{For example, we found that only \jsc{} implements
    tail-call optimization to avoid tail recursion.}\Mar{concrete example!}

  \item \textbf{Not implemented.} False positives of this kind
    manifest when a test fails because it covers a function that is
    part of the official spec, but is not implemented in the target
    engine. For example, at the time of writing, Chakra does not
    implement various properties from the \mcodeid{Symbol} object.

  \item \textbf{Unknown.} This source corresponds to the cases we were
    unable to confidently diagnose the failure.

  %% \item \textbf{Error message mismatch.} Test fails because it
  %%   compares an error message, which is not portable across
  %%   engines. For example, \Igor{
  %%     a test from the engine \jsc{} uses an assert function called
  %%     \CodeIn{shouldThrow} that expects an specific error message. In this test, 
  %%     all engines throws the Error as expected, however only the message 
  %%     on \jsc{} engine match with the string expected in the test case.
  %%   }
\end{itemize}

@@

Table~\ref{tab:false-positives} shows the distribution of false
positives per source. A false positive is a bucket that did not lend
itself in a bug report. The sources of imprecision are as defined in
Section~\ref{sec:transplantation} with the addition of two new
sources, which we did not observe before. The source ``Invalid Input''
indicates that the test violated some part of the specification. For
example, the test indirectly invoked some function with unexpected
arguments\Fix{provide concrete example}. The source ``Upcoming
Feature'' indicates that the test fails because it uses a feature that
is available in the original engine, but it is still not standard, and
the target engine does not support that feature. For example,
\Fix{provide concrete example}

\begin{table}[t]
  \centering
  \caption{\label{tab:false-positives}Distribution of false
    positives buckets per source.}
  \begin{tabular}{crr}
    \toprule
    & \radamsa\ & \quickfuzz\ \\
    Undefined & - & - \\
    Timeout/OME & - & - \\
    Not Implemented & - & - \\
    Upcoming Feature & - & - \\
    Error Message Mismatch & - & - \\    
    Invalid Input & - & - \\    
    \bottomrule     
  \end{tabular}
\end{table}
